\bf Approachable case studies support learning and reproducibility in data science: An example from evolutionary biology

### 2022-02-14 jsdse/Manuscript.tex
barriers

In the next section que describe the barriers to approachability that we identified
on our case study. We addressed these barriers on a teaching material that is
available at
https://mctavishlab.github.io/R\_OpenTree\_tutorials/.

@@

\section*{Identifying hurdles to accessibility}
\label{sec:identifying}

@@

- programming experience/ skills
- specialized jargon knowledge
- use of highly specialized computing jargon and programming techniques;

Some principles of an inclusive syllabus:
- high cognitive load,
- unspecified, unclear or lengthy goals;
- content-focused descriptions instead of user-focused;
- inflexible learning environment;
- unapproachable (cold or intimidating) language;
- and little to no diversity of representation of information

\section*{Addressing hurdles to accessibility: some principles}
\label{sec:addressing}

>>>>

In the next section que describe the barriers to approachability that we identified
on our case study. We addressed these barriers on teaching materials that are
available at
https://mctavishlab.github.io/R\_OpenTree\_tutorials/.

@@

\section*{Identifying barriers to approchable research workflows}
\label{sec:identifying}

Cite carpentries and Mosi

@@

Some principles of an inclusive syllabus:

- high cognitive load/ skill level; (literate programming)

- unspecified, unclear or lengthy goals;(literate programming)

- content-focused descriptions instead of user-focused; (demonstrate errors)

- inflexible learning environment; (make it stable so users can learn whenever is best for them)

- unapproachable (cold or intimidating) language, use of highly specialized computing jargon; (use friendly and informal but respectful language)

- and little to no diversity of representation of information (say the same thing with different images, metaphors, stories)

\section*{Best practices for approachable research workflows}
\label{sec:addressing}
